---
title: "Simple document"
output: github_document
---

I'm an R Markdown document! 

# Problem 1

Here's a **code chunk** that construct the data frame:

```{r data frame}

##load library to apply functions

library(tidyverse)

##construct the data frame

p1data = tibble(
  vec_numeric = runif(10,min=0,max=5),
  vec_char = c("a", "b", "c", "d","e","f","g","h","i","j"),
  vec_factor = factor(c("male", "male", "female", "female","male", "male", "female", "female","male", "male")),
  vec_logical = as.logical(vec_numeric>2)
)

##examine classes

class(p1data$vec_logical)
```

Now I try to take the mean of each variable in my dataframe:

The mean of the random sample is `r mean(p1data$vec_numeric)`. The mean of the logical vector is `r mean(p1data$vec_logical)`. Both the mean of the charater vector and factor vector are `r mean(p1data$vec_char)` and `r mean(p1data$vec_factor)`. 

Here's a **code chunk** that tries to convert logical, char and factor to numerical value:

```{r warning = FALSE, collapse = TRUE}

##convert logical, charater and factor vectors to numberical vectors

Log_to_num = as.numeric(p1data$vec_logical)
Char_to_num = as.numeric(p1data$vec_char)
Fac_to_num = as.numeric(p1data$vec_factor)

##examine classes

class(Log_to_num)
class(Char_to_num)
class(Fac_to_num)
```


```{r char to factor}

##convert character variable to factor 

Char_to_fac = factor(p1data$vec_char)

##exaime classes

class(Char_to_fac)
```

```{r fac to char}

##convert factor variable to character

Fac_to_char = as.character(p1data$vec_factor)

##exaime classes

class(Fac_to_char)

```

# Problem 2

Here is the **code chunk** that construct the data frame

```{r}

p2data = tibble(
  x = rnorm(1000,mean=0),
  y = rnorm(1000,mean=0),
  vec_logical = as.logical(x + y >0),
  
  ##not sure about coersing
  
  Log_to_num_coer = as.numeric (vec_logical),
  Log_to_fac_coer = as.factor(vec_logical)
)

##examine classes


```

The size of the data is `r dim(p2data)`. The mean of the x is `r mean(p2data$x)` and the median of the x is `r median(p2data$x)`. The proportion of the cases for which the logical vector is `r sum(p2data$vec_logical=="TRUE")/length(p2data$vec_logical)`.

Here is the **code chunk** that construct the scatterplot: 

```{r}
library(ggplot2)

ggplot(p2data,
       aes(y = y, x = x, color = vec_logical)) + geom_point()
ggplot(p2data,
       aes(y = y, x = x, color = Log_to_num_coer)) + geom_point()
ggplot(p2data,
       aes(y = y, x = x, color = Log_to_fac_coer)) + geom_point()
```




